Implications of Measurement Errors in Water Use Estimates for Water Management

### 2024-11-13 Writing/manuscript_typst.tex
tex version added

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
% \linenumbers
\usepackage{float}
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Implications of Measurement Errors in Water Use Estimates for Water Management},
  pdfauthor={Taro Mieno; Timothy Foster; Nicholas Brozovic},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Implications of Measurement Errors in Water Use Estimates for Water Management}
\author{Taro Mieno\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:tmieno2@unl.edu}{\nolinkurl{tmieno2@unl.edu}}} \and Timothy Foster\footnote{Department of WWW, University of Manchester, \href{mailto:timothy.foster@manchester.ac.uk}{\nolinkurl{timothy.foster@manchester.ac.uk}}} \and Nicholas Brozovic\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:nbrozovic@nebraska.edu}{\nolinkurl{nbrozovic@nebraska.edu}}}}
\date{}

\begin{document}
\maketitle
\begin{abstract}
abstract here
\end{abstract}

\newpage

@@

\begin{itemize}
\item
  intensity estimation accuracy
\item
  (estimated) intensity-based vs (estimated) area-based (Southern Europe History)
\item
  (estimated) intensity-based vs (true) intensity-based {[}We work on this{]}
\item
  Lack of measurement. Use of water use estimates for water management (current and future). Emergence of Open ET as a substitute.
\end{itemize}

@@

\begin{itemize}
\item
  start a discussion about the implications of the use of mis-measured water use for water use regulation.
\item
  shed lights on unintentional consequences of using estiamtes rather than actual measurements
\end{itemize}

@@

Figure \ref{fig:profit-quota-water-het} below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors. When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use). Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use. However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota. It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix). Not surprisingly, profit losses of using proxy quota increase as measurement error size increases. Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.

@@

{\centering \includegraphics{figures/g_profit_quota_comp_stat}

@@

\caption{The impacts of an increase in the degree of measurement error on profit}\label{fig:profit-quota-water-het}
\end{figure}

We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota. Figure \ref{fig:illust-homegeneous} presents a case with two homegeneous farmers under water and proxy quota. The red dotted lines indicate the effective water quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is 10.94 inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes 29.9 less under the water quota system compared to the proxy quota system. However, Farmer A makes 128.9 more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

@@

{\centering \includegraphics{figures/g_illustration_homogeneous}

@@

\caption{Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers}\label{fig:illust-homegeneous}
\end{figure}

However, as the heterogeneity of farmers increases, comparative advantage of water quota over proxy quota diminishes. While the performance of both systems declines as the level of heterogeneity increases, water quota is affected more so than the proxy quota system. This is because uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous water demand. This is illustrated in Figure \ref{fig:illust-heterogeneous}. In this example, farmer A needs less water than farmer B. Water and proxy quota allocated to the farmers are exactly the same as the previous case. In this example, errors in proxy happened to realize so that more effective water quota is given to farmer B than farmer A. Consequently, proxy quota produces a higher total profit than water quota. Of course, if error happened to go the opposite way, then the performance of proxy quota relative to water quota is even worse compared to the homogeneous case. This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case. Consequently, proxy quota performs relatively better under heterogeneous cases. On average, the positive and negative effects of measurement errors tend to even out. However, proxy quota is never better than water quota \textbf{on average} (see Appendix \ldots{} for mathematical proof).

@@

{\centering \includegraphics{figures/g_illustration_het}

@@

\caption{Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers}\label{fig:illust-heterogeneous}
\end{figure}

@@

Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation. Figure \ref{fig:trading-profit} presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems. As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed. This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota.

@@

{\centering \includegraphics{figures/g_trade_effect_profit}

@@

\caption{Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed}\label{fig:trading-profit}
\end{figure}

Figure \ref{fig:trading-profit-illustration} illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in Figure \ref{fig:illust-homegeneous}. In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems. No water quota trading would happen as the marginal profit of water is already equated at water use of 7. Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively. Once trading of proxy quota is alllowed, farmer A would buy 1.85 proxy quota from farmer B. At these production levels, the marginal profit of quota (not water) are equated acros the farmers and no further transfer between them would happen. Trading of proxy quota improves the overall profit to 920.08 \$/acre from 831.94 \$/acre.

@@

{\centering \includegraphics{figures/g_illustration_homogeneous_with_trade}

@@

\caption{Illustration of the benefits of trading quota}\label{fig:trading-profit-illustration}
\end{figure}

While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use. In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading. Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use. Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix \ldots{} for a mathematical proof). However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \ref{fig:trading-profit}. This point is well-illustrated in Figure \ref{fig:trading-profit-illustration}, where total profit per acre is 930.91 and 920.08 under the water-quota and proxy-quota trading system, respsectively.

Figure \ref{fig:trading-profit} presents the simualtion results of proxy-quota and water-quota trading systems added to Figure \ref{fig:profit-quota-water-het}. As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier). Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.

@@

Figure \ref{fig:distributional-equity} presents the cumulative probability of the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system. If farmers make just as much profir under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1. For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system. At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estiamtes are much higher than their actual water use. At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estiamtes are much lower than their actual water use. Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves. If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment. Allowind quota trading greatly diminishes the distributional inequality, though not completely. This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.

@@

{\centering \includegraphics{figures/g_profit_ratio}

@@

\caption{Distribution of profit under various regulation systems}\label{fig:distributional-equity}
\end{figure}

@@

Three different sets of the collections of crop-water production functions are generated that vary in the degree of heterogeneity in unconstrained optimal water use (\(w^*\)). Under no-heterogeneity set, farmers share exactly the same profuction function (the same value of \(\phi_i\), \(\alpha_i\), and \(\beta_i\)). Unde the medium-heterogeneity set, model parameters vary and so does \(w^*\). Under the high-heterogeneity set, the variance of \(w^*\) becomes even greater. The distribution of \(w^*\) for each of the sets is presented in Figure \ref{fig:dist-opt-w}.

@@

Three different sets of the distribution of \(\eta\) are considered that vary in the degree of heterogeneity in \(\eta\): low, medium, and high. For all the sets, \(E[\eta] = 1\) (or equivalently \(E[\mu] = 0\)), meaning that water use estimation is ubiased. A sample of the empirical (realized) distribution of \(\eta\) for each of the sets is presented in Figure \ref{fig:dist-eta}.

@@

\clearpage

\appendix

@@

{\centering \includegraphics{figures/g_opt_w_dist}

@@

\caption{Distribution of optimal water use under no water use constraints}\label{fig:dist-opt-w}
\end{figure}

\subsection{Distribution of water-proxy conversion factor}\label{distribution-of-water-proxy-conversion-factor}

\clearpage

  \bibliography{DRA.bib}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Implications of Measurement Errors in Water Use Estimates for Water Management},
  pdfauthor={Taro Mieno; Timothy Foster; Nicholas Brozovic},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Implications of Measurement Errors in Water Use Estimates for
Water Management}
\author{Taro Mieno\footnote{University of Nebraska-Lincoln, Email:
  tmieno2@unl.edu} \and Timothy Foster\footnote{University of Manchester} \and Nicholas
Brozovic\footnote{University of Nebraska-Lincoln}}
\date{}

\begin{document}
\maketitle

@@

\begin{itemize}
\item
  Use of satellite imagery in water management in general

  \begin{itemize}
  \tightlist
  \item
    water theft detection in Australia (Nature Water, Adam Loch)
  \end{itemize}
\item
  intensity estimation accuracy
\item
  (estimated) intensity-based vs (estimated) area-based (Southern Europe
  History)
\item
  (estimated) intensity-based vs (true) intensity-based {[}We work on
  this{]}
\item
  Lack of measurement. Use of water use estimates for water management
  (current and future). Emergence of Open ET as a substitute.
\end{itemize}

@@

\begin{itemize}
\item
  start a discussion about the implications of the use of mis-measured
  water use for water use regulation.
\item
  shed lights on unintentional consequences of using estimates rather
  than actual measurements
\end{itemize}

@@

Figure~\ref{fig-profit-quota-water-het} illustrates the profit from
agricultural production as a function of actual water use, comparing
water quotas and proxy quotas across three levels of production
heterogeneity and varying sizes of measurement errors. When there is no
production heterogeneity among farmers, the water quota is the most
cost-effective mechanism to achieve a targeted reduction in water use
(yielding the highest profit for a given level of actual water use). In
this scenario, the proxy quota with unbiased measurement errors performs
worse than the water quota due to the asymmetry in downside and upside
risk of water use. However, as production heterogeneity increases, the
comparative advantage of water quotas over proxy quotas diminishes.

It is demonstrated (proof in Appendix) that water quotas consistently
outperform proxy quotas on average, regardless of production
heterogeneity, when measurement errors are independent and the
production function is concave. As expected, the profit losses
associated with proxy quotas increase as the size of measurement errors
grows. Furthermore, the profit loss from using proxy-based quotas tends
to become more pronounced as total realized water use decreases.

@@

\centering{

\includegraphics[width=1.6in,height=\textheight]{figures/g_profit_quota_comp_stat.png}

@@

\caption{\label{fig-profit-quota-water-het}The impacts of an increase in
the degree of measurement error on profit}

\end{figure}%

Grafton et al. (2018)

We now look at simple two-farm examles to build intuition behind the
profit loss due to the use of proxy quota in place of water quota.
Figure~\ref{fig-illust-homegeneous} presents a case with two homegeneous
farmers under water and proxy quota. The red dotted lines indicate the
effective water quota. Under the water quota system, both farmers
receive 7 inches of water quota. Since the unconstrained profit
maximizing water use is 10.94 inches, both farmers use up all the
allocated quota and use 10 inches of water. Under the proxy quota
system, they are allocated the same amount of proxy quota. However,
measurement error in proxy quota resulted in effective water quota of 4
and 10 inches for farmer A and B, respectively. Both farmers use their
allocated amout of water. Under both proxy and water quota systems, the
total water use is 14 inches. Farmer B makes 29.9 less under the water
quota system compared to the proxy quota system. However, Farmer A makes
128.9 more under the water quota system compared to the proxy quota
system. This comes from an important nature of crop production with
respsect to water: declining marginal impact of water on crop yield. As
can be seen in the profit-water relationship, removing an inch of water
from 6 inches has much larger negative impact compared to revmoing an
inch of water from 10 inches.

@@

\centering{

\includegraphics[width=1.73in,height=\textheight]{figures/g_illustration_homogeneous.png}

@@

\caption{\label{fig-illust-homegeneous}Illustration of profit loss due
to the use of proxy for quota-based regulation: a case of homegeneous
producers}

\end{figure}%

However, as the heterogeneity of farmers increases, comparative
advantage of water quota over proxy quota diminishes. While the
performance of both systems declines as the level of heterogeneity
increases, water quota is affected more so than the proxy quota system.
This is because uniform quota now acts like heterogeneous quota under
homogeneous production function because the same quota is given to
farmers with heterogeneous water demand. This is illustrated in
Figure~\ref{fig-illust-heterogeneous}. In this example, farmer A needs
less water than farmer B. Water and proxy quota allocated to the farmers
are exactly the same as the previous case. In this example, errors in
proxy happened to realize so that more effective water quota is given to
farmer B than farmer A. Consequently, proxy quota produces a higher
total profit than water quota. Of course, if error happened to go the
opposite way, then the performance of proxy quota relative to water
quota is even worse compared to the homogeneous case. This is a big
contrast to the homogeneous case because water quota is always better
than proxy quota in that case. Consequently, proxy quota can perform
relatively better under heterogeneous cases. On average, the positive
and negative effects of measurement errors tend to even out. However,
proxy quota is never better than water quota \textbf{on average} (see
Appendix \ldots{} for mathematical proof).

@@

\centering{

\includegraphics[width=1.73in,height=\textheight]{figures/g_illustration_het.png}

@@

\caption{\label{fig-illust-heterogeneous}Illustration of profit loss due
to the use of proxy for quota-based regulation: a case of heterogeneous
producers}

\end{figure}%

@@

Allowing quota to be traded among farmers can dramatically change the
relative performance of the water- and quota-based regulation.
Figure~\ref{fig-trading-profit} presents profit for water-based quota,
proxy-based quota, water-based quota trading, and proxy-based quota
trading regulation systems. As shown in the figure, the disadvantage of
using proxy almost disappears when trading of quota is allowed. This is
because the inefficiencies in quota allocations are resolved through
trading of quota whether it is water or proxy quota.

@@

\centering{

\includegraphics[width=1.6in,height=\textheight]{figures/g_trade_effect_profit.png}

@@

\caption{\label{fig-trading-profit}Comparison of profit from
agricultural production between the water and quota systems when quota
trading is allowed}

\end{figure}%

Figure~\ref{fig-trading-profit-illustration} illustrates the impact of
allowing for trading proxy quota using the case of two homogeneous
farmers illustrated in Figure~\ref{fig-illust-homegeneous}. In this
illustration, the same water quota of 7 is allocated for both farmers
under the water-based systems. No water quota trading would happen as
the marginal profit of water is already equated at water use of 7. Under
the proxy-base quota system, proxy quota of 7 is allocated for both
farmers, but the effective water quota for farmers A and B are 4 and 7,
respectively. Once trading of proxy quota is alllowed, farmer A would
buy 1.85 proxy quota from farmer B. At these production levels, the
marginal profit of quota (not water) are equated acros the farmers and
no further transfer between them would happen. Trading of proxy quota
improves the overall profit to 920.08 \$/acre from 831.94 \$/acre.

@@

\centering{

\includegraphics[width=1.73in,height=\textheight]{figures/g_illustration_homogeneous_with_trade.png}

@@

\caption{\label{fig-trading-profit-illustration}Illustration of the
benefits of trading quota}

\end{figure}%

While water-quota and proxy-quota trading perform about the same,
water-quota always leads to a higher total profit for a given level of
realized water use. In other words, to achieve a certain water use goal,
water-quota trading is always to more cost-effective than proxy-quota
trading. Under water-quota trading, the margial profit of water is
equalized across the farmers, which is a necessary condition to achieve
the highest profit for a given level of total water use. Under
proxy-quota trading, the marginal profit of proxy is equalized across
the farmers, not the margial profit of water (See Appendix \ldots{} for
a mathematical proof). However, it is worth emphasizing that the
inefficiency caused by the use of proxy is likely to be minimal as shown
in Figure~\ref{fig-trading-profit}. This point is well-illustrated in
Figure~\ref{fig-trading-profit-illustration}, where total profit per
acre is 930.91 and 920.08 under the water-quota and proxy-quota trading
system, respsectively.

Figure~\ref{fig-trading-profit} presents the simualtion results of
proxy-quota and water-quota trading systems added to
Figure~\ref{fig-profit-quota-water-het}. As you can see at all levels of
production heterogeneity levels and the degres of measurement errors,
proxy-quota and water-quota trading systems perform almost identical at
all levels of realized water use (water-quota trading is always slightly
better than proxy-quota trading as explained earlier). Not surprisingly,
the benefit of allowing for trading is greater when the degree of
measurement errors is larger.

@@

Figure~\ref{fig-distributional-equity} presents the cumulative
probability of the ratio of profit under the proxy-based relative to
water-based system for quota (red) and permit trading (blue). Ratio of
less than 1 indicates making less profit under the proxy-based system
compared to the water-based system. If farmers make just as much profit
under proxy-based regulation compared to water-based regulation, then
the cumulative probability line would be a vertical line at 1. For
example, under the high degree of measurement error and medium
heterogenenity scenario, some farmers would make about the half of what
they would make under the water quota system. At the lower end of the
distribution are farmers who would be constrained severely by water
quota, but whose water use estiamtes are much higher than their actual
water use. At the higher end of the distribution are farmers who would
be constrained by water quota, but whose water use estiamtes are much
lower than their actual water use. Famres who suffer significantly under
the quota system can develop strong dissatisfaction of the quota-based
regulation system, which in turn may lead to installing water meter
themselves. If they discover the over-estimation of their water use,
they may appeal to legal actions against the administrator for their
unfair treatment. Allowind quota trading greatly diminishes the
distributional inequality, though not completely. This is because
unfortunate farmers who suffered from over-estimation of their water use
can now at least purchase proxy quota to increase their production
level.

@@

\centering{

\includegraphics[width=1.6in,height=\textheight]{figures/g_profit_ratio.png}

@@

\caption{\label{fig-distributional-equity}Distribution of profit under
various regulation systems}

\end{figure}%

@@

Three different sets of the collections of crop-water production
functions are generated that vary in the degree of heterogeneity in
unconstrained optimal water use (\(w^*\)). Under no-heterogeneity set,
farmers share exactly the same profuction function (the same value of
\(\phi_i\), \(\alpha_i\), and \(\beta_i\)). Unde the
medium-heterogeneity set, model parameters vary and so does \(w^*\).
Under the high-heterogeneity set, the variance of \(w^*\) becomes even
greater. The distribution of \(w^*\) for each of the sets is presented
in Figure~\ref{fig-dist-opt-w}.

@@

Three different sets of the distribution of \(\eta\) are considered that
vary in the degree of heterogeneity in \(\eta\): low, medium, and high.
For all the sets, \(E[\eta] = 1\) (or equivalently \(E[\mu] = 0\)),
meaning that water use estimation is ubiased. A sample of the empirical
(realized) distribution of \(\eta\) for each of the sets is presented in
\textbf{?@fig-dist-eta}.

@@

\section*{(APPENDIX) Appendix}\label{appendix-appendix}
\addcontentsline{toc}{section}{(APPENDIX) Appendix}

@@

\centering{

\includegraphics[width=1.6in,height=\textheight]{figures/g_opt_w_dist.png}

@@

\caption{\label{fig-dist-opt-w}Distribution of optimal water use under
no water use constraints}

\end{figure}%

\subsection*{Distribution of water-proxy conversion
factor}\label{distribution-of-water-proxy-conversion-factor}
\addcontentsline{toc}{subsection}{Distribution of water-proxy conversion
factor}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-grafton2018paradox}
Grafton, R. Q., J. Williams, C. J. Perry, F. Molle, C. Ringler, P.
Steduto, B. Udall, et al. 2018. {``The Paradox of Irrigation
Efficiency.''} \emph{Science} 361 (6404): 748--50.

\end{CSLReferences}
